Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-06 paper.tex
Titulos cambiados
acks

\section{GPGPU Shared Service in OpenStack}
In this section is explained all the work related to OpenStack that has been done, from the development of an external module to handle remote GPUs to the physical setup and its testing.
\subsection{Managing remote GPUs with OpenStack}
The main idea of this solution is to reach the scenario that could be seen in Figure~\ref{fig:external}, where a new shared service takes part in to the OpenStack Architecture.
This new service is in charge of GPGPU computation, bringing more flexibility when it comes to GPUs.
As it is shown in Figure~\ref{fig:internal}, we have altered the OpenStack original Dashboard with a new parser, 
which split the HTTP query in order to make use of both, the GPGPU API for everything related to GPUs, and the nova API for the rest of the computation. 
The new GPGPU Service has brought a new feature which brings more flexibility when managing GPUs, from now on, we can create ``GPU-pools''. 
A ``GPU-pool'' is a set of independent GPUs (logically disattached from the nodes) that can be assigned to one or more instances.

@@

\section*{\uppercase{Acknowledgements}}
The researchers from the Universidad Jaume~I were supported by Universitat Jaume I research project (P11B2013-21), project
TIN2011-23283 and~FEDER.

>>>>

\section{GPGPU Shared Service in OpenStack}
In this section all the work related to OpenStack that has been done is explained, from the development of an external module to handle remote GPUs to the physical setup and its testing.
\subsection{Managing remote GPUs with OpenStack}
The main idea of this solution is to reach the scenario that could be seen in Figure~\ref{fig:external}, where a new shared service takes part in to the OpenStack Architecture.
This new service is in charge of GPGPU computation, bringing more flexibility when it comes to GPUs.
As it is shown in Figure~\ref{fig:internal}, we have altered the OpenStack original Dashboard with a new parser, 
which split the HTTP query in order to make use of both, the GPGPU API for everything related to GPUs, and the nova API for the rest of the computation. 
The new GPGPU Service has brought a new feature which brings more flexibility when managing GPUs, from now on, we can create ``GPU-pools''. 
A ``GPU-pool'' is a set of independent GPUs (logically disattached from the nodes) that can be assigned to one or more instances.

@@

\section*{\uppercase{Acknowledgements}}
The authors want to thank the IT members of the department Vicente Roca and Gustavo Edo for the given help.
The researchers were supported by Universitat Jaume I research project (P11B2013-21), project
TIN2011-23283 and~FEDER.
